### 2016-08-23 analysis-note-v2/RTPC.tex
more updates to the RTPC and the DVCS checks, and updated the ALU tables after the 4D background subtraction

 The $\vec{B}$ field is generated by the solenoid. Figure \ref{fig:B_MAP} shows the magnetic field vectors in the different regions of the RTPC. The presence of the magnetic field enables us to deduce the momentum of a charged particle from the curvature of its track and the known magnetic field.
% from:
%\begin{equation}
%p = R q |\overrightarrow{B}| sin(\theta)
%\end{equation}
%where R is the radius of the track's curvature, q and $\theta$ are the charge and the polar angle of the %particle.

@@

\begin{figure}[tbp]
\centering
\vspace{-0.1in}
\includegraphics[scale=0.38]{fig_rtpc/RTPC_track.png}
\vspace{-0.1in}
\caption{Schematic of a segment of the RTPC in a plane perpendicular to the beam line, with a $^4He$ track (in green) crossing the volume. See the text for description of the various elements and notations.} 
\label{fig:RTPC_track}
\end{figure}

@@

An algorithm was developed to remove hits corresponding to this noise without suppressing good hits.  First, the ADC vs TDC noise curve was parameterized.  Next, for every event and channel independently, the number of hits falling on this curve is counted.  If a significant number of hits lie far above or below the noise curve, no rejection is performed.  If most of the hits below TDC=30 fall on the noise curve, all hits below TDC=30 are rejected for that channel.  Figure \ref{fig:Adcvstdcnoise} shows the effect of this noise reduction for one very noisy pad.

The result of this algorithm is 5$\%$ more good tracks reconstructed, with improved signal to background ratio, as can be seen in figure \ref{fig:noise_edist_}. 
Further, this allowed to recover 40 channels that had previously been ignored due to high occupancies before this noise rejection.

\begin{figure}[tbp]
%\hspace{-0.4in}
\includegraphics[scale=0.3]{fig_rtpc/noisy_pad_before_rejection.png}
\includegraphics[scale=0.3]{fig_rtpc/noisy_pad_after_rejection.png}
%\vspace{-0.3in}
\caption{The integrated ADC vs. TDC of the hits for good tracks before (left) and after (right) the oscillatory noise reduction, for a particular pad with strong noise. The event sample and color scales are identical in both plots.}
\label{fig:Adcvstdcnoise}
\end{figure}

@@

\clearpage
\section{Tracking resolution}
~~~~The RTPC tracking resolution is defined as the spread of the reconstructed 
track vertex, angles and momentum with respect to their true values. In the EG6 
experiment, we use the cleanly identified elastic events to estimate the RTPC 
resolutions. The CLAS detector nominally provides electron detection with an 
angular resolution around 1 and 4 mrad in $\theta$ and $\phi$, and a momentum 
resolution ($\frac{\Delta p}{p}$) around 0.5$\%$ \cite{CLASref}. The z-vertex 
resolution of about 3 mm for an extended target in the presence of the 
solenoid, as can be observed experimentally from the target window, figure 
\ref{fig:electron_z_vertex_res}. \\
\begin{figure}[tbp]
   \centering
   \includegraphics[height=6.2cm]{fig_rtpc/clas_z_resolution.png}
   \caption{ z-vertex of scattered electrons from the downstream window of the 
   target. The z-vetex resolution of CLAS here is about 3 mm.}
   \label{fig:electron_z_vertex_res}
\end{figure}

>>>>

The $\vec{B}$ field is generated by the solenoid. Figure \ref{fig:B_MAP} shows 
the magnetic field vectors in the different regions of the RTPC. The presence 
of the magnetic field enables us to deduce the momentum of a charged particle 
from the curvature of its track and the known magnetic field.
% from:
%\begin{equation}
%p = R q |\overrightarrow{B}| sin(\theta)
%\end{equation}
%where R is the radius of the track's curvature, q and $\theta$ are the charge 
%and the polar angle of the %particle.

@@

\begin{figure}[tbp]
\centering
\vspace{-0.1in}
\includegraphics[scale=0.38]{fig_rtpc/RTPC_track.png}
\vspace{-0.1in}
\caption{Schematic of a segment of the RTPC in a plane perpendicular to the 
beam line, with a $^4He$ track (in green) crossing the volume. See the text for 
description of the various elements and notations. $sdist$ and $edist$ are 
defined position as shown in this sketch.} \label{fig:RTPC_track}
\end{figure}

@@

An algorithm was developed to remove hits corresponding to this noise without 
suppressing good hits.  First, the ADC vs TDC noise curve was parameterized.  
Next, for every event and channel independently, the number of hits falling on 
this curve is counted.  If a significant number of hits lie far above or below 
the noise curve, no rejection is performed.  If most of the hits below TDC=30 
fall on the noise curve, all hits below TDC=30 are rejected for that channel.  
Figure \ref{fig:Adcvstdcnoise} shows the effect of this noise reduction for one 
very noisy pad. The result of this algorithm is 5$\%$ more good tracks 
reconstructed, with improved signal to background ratio, as can be seen in 
figure \ref{fig:noise_edist_}.  Further, this allowed to recover 40 channels 
that had previously been ignored due to high occupancies before this noise 
rejection.

\begin{figure}[tbp]
%\hspace{-0.4in}
\includegraphics[scale=0.3]{fig_rtpc/noisy_pad_before_rejection.png}
\includegraphics[scale=0.3]{fig_rtpc/noisy_pad_after_rejection.png}
%\vspace{-0.3in}
\caption{The integrated ADC vs. TDC of the hits for good tracks before (left) 
and after (right) the oscillatory noise reduction, for a particular pad with 
strong noise. The color scale on the z-axis is for the hit yield and identical 
in both plots as well as the event sample.}
\label{fig:Adcvstdcnoise}
\end{figure}

@@

\clearpage
\section{Tracking resolution}
~~~~The RTPC tracking resolution is defined as the spread of the reconstructed 
track vertex, angles and momentum with respect to their true values. In the EG6 
experiment, we use the cleanly identified elastic events to estimate the RTPC 
resolutions. The CLAS detector nominally provides electron detection with an 
angular resolution around 1 and 4 mrad in $\theta$ and $\phi$, and a momentum 
resolution ($\frac{\Delta p}{p}$) around 0.5$\%$ \cite{CLASref}. The z-vertex 
resolution is about 3 mm for an extended target in the presence of the 
solenoid, as can be observed experimentally from the target window, figure 
\ref{fig:electron_z_vertex_res}. \\
\begin{figure}[tbp]
   \centering
   \includegraphics[height=6.2cm]{fig_rtpc/clas_z_resolution.png}
   \caption{ z-vertex of scattered electrons from the downstream window of the 
   target. The z-vetex resolution of CLAS here is about 3 mm.}
   \label{fig:electron_z_vertex_res}
\end{figure}

### 2016-08-23 analysis-note-v2/analysis-2.tex
more updates to the RTPC and the DVCS checks, and updated the ALU tables after the 4D background subtraction

~\newpage
\paragraph{DVCS characteristics}
\begin{itemize}
\item $Q^{2}$ > 1 GeV$^{2}$: to ensure that the interaction occurs at the partonic level and the applicability of the factorization in the DVCS  handbag diagram.
%\item The invariant mass of the system of the virtual photon and the target 
   %proton is greater than $2~GeV/c{^2}$. This cut avoids the region of 
   %excitation of the proton to resonances.
\item $ -t > -t_{min}$: the transferred momentum squared to the recoil $^{4}He$ has to be greater than a minimum value defined by the kinematics of the beam and the scattered electron as:
\begin{equation}
   t_{min} = - Q^{2} \frac{2(1- x_{A})(1 - \sqrt{1 + \epsilon ^{2}}) + \epsilon 
   ^{2}}{4 x_{A}(1-x_{A})+ \epsilon ^{2}},\\
\end{equation}
where $\epsilon ^{2} = \frac{4M^{2}_{^4He}x^{2}_{A}}{Q^{2}}$, $x_{A} = \frac{M_{p}\cdot x_{B}}{M_{^4He}}$ and $M_{p}$ ($M_{^4He}$) is the proton ($^{4}He$) mass.\\

In the case of the proton DVCS, the variable $x_{A}$ is replaced by the Bjorken $x_{B}$ in the formula for $t_{min}$.

@@

\begin{figure}[tbp]
      \includegraphics[height=5.0cm]{fig_dvcs/photon_energy_coh_sim.png}
      \includegraphics[height=5.5cm]{fig_dvcs/photon_energy_incoh_sim.png}
          \caption{The energy distribution of the simulated coherent, on top, 
          and incoherent, on bottom, DVCS photons.}
          \label{fig:energy_dvcs_photons}
\end{figure}

\end{itemize}

\paragraph{Exclusivity cuts}

@@

As presented in the previous section, we construct two-dimensional bins: $Q^2$-$\phi$, $x_B$-$\phi$ and -$t$-$\phi$. Thus, for each bin in $Q^2$, $x_B$ and $-t$, we assume that the acceptance ratio does not change a lot within the bin range and we construct the one-dimensional acceptance ratio as a function of $\phi$. The latter is used to perform the background subtraction as shown in equations \ref{equ_back_1} and \ref{equation: background_equ}.

@@

\begin{figure}[tp]
\centering
\includegraphics[scale=0.30]{fig_dvcs/epgamma_eppi0_Q2.png}
\includegraphics[scale=0.30]{fig_dvcs/epgamma_eppi0_xB.png}
\includegraphics[scale=0.30]{fig_dvcs/epgamma_eppi0_t.png}
\includegraphics[scale=0.30]{fig_dvcs/epgamma_eppi0_Phi.png}
\caption{The incoherent channel acceptance ratios as a function of the 
kinematic variables: $Q^{2}$ (top left), $x_{B}$ (top right), $-t$ (bottom 
left), and $\phi$ (bottom right).  }
\label{fig:incoh_acceptance _ratios}
\end{figure}

@@

\begin{figure}[h!]
\includegraphics[scale=0.31]{fig_dvcs/e4Hegamma_M2_Mis_sig.png}
\includegraphics[scale=0.31]{fig_dvcs/e4Hegamma_M2_Mis_sig.png}
\includegraphics[scale=0.31]{fig_dvcs/e4Hegamma_e4Hepi0_Phi_2.png}
\hspace{-0.2in}\includegraphics[scale=0.31]{fig_dvcs/R_epgamma_eppi0_Phi.png}
\includegraphics[scale=0.31]{fig_dvcs/BSA_Coherent_sigmas.png}
\includegraphics[scale=0.31]{fig_dvcs/BSA_InCoherent_sigmas.png}
\caption{The systematic uncertainties stemming from the DVCS selection cuts in 
the coherent (left column) and the incoherent (right column) channels. On the 
top: the missing mass squared of $e^{4}He\gamma$ and $ep\gamma$. The different 
vertical coloured lines indicate the different cuts: 1$\sigma$, 2$\sigma$, ...  
5$\sigma$. In the middle: the coherent (incoherent) acceptance ratios versus 
$\phi$ for the different configurations of the cuts. On the bottom: the 
reconstructed $A_{LU}$ as a function of $\phi_{h}$ for the different cut 
widths.}
\label{fig:cuts_e4Hegamma_M2_Mis}
\end{figure}

>>>>

~\newpage
\paragraph{DVCS characteristics}
\begin{itemize}
 \item $Q^{2}$ > 1 GeV$^{2}$: to ensure that the interaction occurs at the 
    partonic level and the applicability of the factorization in the DVCS  
    handbag diagram.
\item $ -t > -t_{min}$: the transferred momentum squared to the recoil $^{4}He$ 
   has to be greater than a minimum value defined by the kinematics of the beam 
   and the scattered electron as:
\begin{equation}
   t_{min} = - Q^{2} \frac{2(1- x_{A})(1 - \sqrt{1 + \epsilon ^{2}}) + \epsilon 
   ^{2}}{4 x_{A}(1-x_{A})+ \epsilon ^{2}},\\
\end{equation}
where $\epsilon ^{2} = \frac{4M^{2}_{^4He}x^{2}_{A}}{Q^{2}}$, $x_{A} = 
\frac{M_{p}\cdot x_{B}}{M_{^4He}}$ and $M_{p}$ ($M_{^4He}$) is the proton 
($^{4}He$) mass.\\

In the case of the proton DVCS, the variable $x_{A}$ is replaced by the Bjorken 
$x_{B}$ in the formula for $t_{min}$. Figure \ref{fig:tmin_both} presents 
$t_{min}$ distributions for both DVCS channels.

\item In the case of the incoherent DVCS channel, we apply a cut on the 
   invariant mass of the virtual photon and the target proton system to be
   greater than $2~GeV/c{^2}$. This cut avoids the region of excitation of the 
   proton to resonances.

@@

\begin{figure}[tbp]
\includegraphics[height=5.0cm]{fig_rtpc/updates/tmin_coh.png}
\includegraphics[height=5.0cm]{fig_rtpc/updates/tmin_incoh.png}
\caption{Coherent (left) and incoherent (right) -$t_{min}$ distributions 
calculated for the experimentally selected DVCS events. We use the experimental 
$Q^{2}$ and $x_{B}$ of the individual events. }
\label{fig:tmin_both}
 \end{figure}

\begin{figure}[tbp]
      \includegraphics[height=5.0cm]{fig_dvcs/photon_energy_coh_sim.png}
      \includegraphics[height=5.5cm]{fig_dvcs/photon_energy_incoh_sim.png}
      \caption{The energy distribution of the simulated coherent (left) and 
      incoherent (right) DVCS photons.}
      \label{fig:energy_dvcs_photons}
\end{figure}
\end{itemize}

\newpage
\paragraph{Exclusivity cuts}

@@

@@

\begin{figure}[tp]
\centering
\includegraphics[scale=0.30]{fig_dvcs/epgamma_eppi0_Q2.png}
\includegraphics[scale=0.30]{fig_dvcs/epgamma_eppi0_xB.png}
\includegraphics[scale=0.30]{fig_dvcs/epgamma_eppi0_t.png}
\includegraphics[scale=0.30]{fig_dvcs/epgamma_eppi0_Phi.png}
\caption{The incoherent channel acceptance ratios as a function of the 
kinematic variables: $Q^{2}$ (top left), $x_{B}$ (top right), $-t$ (bottom 
left), and $\phi$ (bottom right).}
\label{fig:incoh_acceptance _ratios}
\end{figure}

As presented in the previous section, we construct two-dimensional bins: 
$Q^2$-$\phi$, $x_B$-$\phi$ and -$t$-$\phi$. Thus, for each bin in $Q^2$, $x_B$ 
and $-t$, we assume that the acceptance ratio does not change a lot within the 
bin range and we construct the one-dimensional acceptance ratio as a function 
of $\phi$. We also carried out four-dimensional background subtraction, in 
which the acceptance ratio has been extracted from simulation as a function of 
$Q^2$, $x_B$, -$t$, and $\phi$. The difference between the reconstructed 
beam-spin asymmetries using two-dimensional and four-dimensional background 
subtraction are presented in figures \ref{fig:coh_binning} and 
\ref{fig:incoh_binning} for the coherent and the incoherent DVCS channels.  
Even though the two-dimensional subtraction is a good approximation, a 
four-dimensional subtraction is applied on the final results presented next 
chapter.

\begin{figure}[tbp]
   \centering
    \includegraphics[height=6.0cm]{fig_rtpc/updates/BSA_Coherent_xB.png}
    \includegraphics[height=6.0cm]{fig_rtpc/updates/diff_BSA_Coherent_xB_2.png}
    \caption{On top: the reconstruct coherent beam-spin asymmetries as a 
    function of $\phi$ in $x_{B}$ bins using two-dimensional (in blue) and 
 four-dimensional (in green) background subtraction.  On bottom: the difference 
 between the two asymmetries as a function of $\phi$.}
    \label{fig:coh_binning}
    \end{figure}

    \begin{figure}[tbp]
       \centering
    \includegraphics[height=5.2cm]{fig_rtpc/updates/BSA_InCoherent_xB.png}
    \includegraphics[height=5.2cm]{fig_rtpc/updates/diff_BSA_InCoherent_xB_2.png}
    \caption{On top: the reconstruct incoherent beam-spin asymmetries using    
    two-dimensional (in blue) and four-dimensional (in green) background 
 subtraction.  On bottom: the difference between the two asymmetries as a 
 function of $\phi$.}
    \label{fig:incoh_binning}
    \end{figure}

Regarding other backgrounds, the procedures carried out in this work followed 
the same guidelines as for DVCS analysis on the nucleon. The neutral pion 
production occurs "without threshold" as seen from the $eHe\gamma$ sample, 
meaning that the contamination from $eHe\pi^0$ with one photon lost is 
distributed all the way down to the DVCS, in the limit where the second photon 
energy becomes negligible in the lab. Single charged pion production occurs 
with a small threshold but is inconsistent with the already detected particles 
($e$ and $^{4}$He). Two pion production is entirely cleaned up by the 
exclusivity cuts. Scattering from the windows is excluded by the vertex cuts.  
As far as accidental, we correct for that as presented in the following 
section.

@@

\begin{figure}[h!]
\includegraphics[scale=0.31]{fig_dvcs/e4Hegamma_M2_Mis_sig.png}
\includegraphics[scale=0.31]{fig_dvcs/epgamma_M2_Mis_sig.png}
\includegraphics[scale=0.31]{fig_dvcs/e4Hegamma_e4Hepi0_Phi_2.png}
\hspace{-0.2in}\includegraphics[scale=0.31]{fig_dvcs/R_epgamma_eppi0_Phi.png}
\includegraphics[scale=0.31]{fig_dvcs/BSA_Coherent_sigmas.png}
\includegraphics[scale=0.31]{fig_dvcs/BSA_InCoherent_sigmas.png}
\caption{The systematic uncertainties stemming from the DVCS selection cuts in 
the coherent (left column) and the incoherent (right column) channels. On the 
top: the missing mass squared of $e^{4}He\gamma$ and $ep\gamma$. The different 
vertical coloured lines indicate the different cuts: 1$\sigma$, 2$\sigma$, ...  
5$\sigma$. In the middle: the coherent (incoherent) acceptance ratios versus 
$\phi$ for the different configurations of the cuts. On the bottom: the 
reconstructed $A_{LU}$ as a function of $\phi_{h}$ for the different cut 
widths.}
\label{fig:cuts_e4Hegamma_M2_Mis}
\end{figure}

### 2016-08-23 analysis-note-v2/data_analysis.tex
more updates to the RTPC and the DVCS checks, and updated the ALU tables after the 4D background subtraction

\subsubsection*{IC photons}
For IC photons, we use the following cuts:
\begin{itemize}
\item IC fiducial cuts: the photons which hit the edges of the IC deposit only part of their energies within the calorimeter. For this reason, we reject the photons which hit the innermost or the outermost rings of the IC. Figure \ref{fig:photons_IC_XY_2} illustrates this cut \cite{FX_thesis}.

\item M\o ller electrons reduction: a two-dimensional plot of photon polar angles as a function of the energy shows an overcrowded region at low $\theta$ and low energy. This can be seen in figure \ref{fig:photons_IC_theta_En_1}. This region is mostly populated by the M\o ller electrons and must be excluded from the analysis. We optimized a linear cut for this region, shown by the black dashed line. The vertical extension of this line shows the minimum energy cut ($E_{\gamma}$ > 300 MeV).
\item We do not apply any timing cut on the IC because its timing is not functionning properly for certain channels. Therefore, applying a timing cut would add inefficient regions in the detector that we wanted to avoid. Therefore, we rely mainly on exclusivity cuts to remove any potential contamination.

@@

The fastmc is applied to the Monte-Carlo generated 
$^{4}He$ for the channels $e^{4}He\gamma$ and $e^{4}He\pi^{0}$. The other 
particles are fed to GSIM through the previously mentioned 
simulation-reconstruction chain procedures.

>>>>

\subsubsection*{IC photons}
For IC photons, we use the following cuts:
\begin{itemize}
\item IC fiducial cuts: the photons which hit the edges of the IC deposit only 
   part of their energies within the calorimeter. For this reason, we reject 
   the photons which hit the innermost or the outermost rings of the IC.  
   Figure \ref{fig:photons_IC_XY_2} illustrates this cut \cite{FX_thesis}.
\item M\o ller electrons reduction: a two-dimensional plot of photon polar 
   angles as a function of the energy shows an overcrowded region at low 
   $\theta$ and low energy. This can be seen in figure 
   \ref{fig:photons_IC_theta_En_1}. This region is mostly populated by the M\o 
   ller electrons and must be excluded from the analysis. We optimized a linear 
   cut for this region, shown by the black dashed line. The vertical extension 
   of this line shows the minimum energy cut ($E_{\gamma}$ > 300 MeV).
\item We do not apply any timing cut to select the photons in the IC because 
   its timing is not functioning properly for certain channels. Therefore, 
   applying a timing cut would add inefficient regions in the detector that we 
   wanted to avoid.  Therefore, we rely mainly on exclusivity cuts to remove 
   any potential contamination.

@@

The fastmc is applied to the Monte-Carlo generated $^{4}He$ for the channels 
$e^{4}He\gamma$ and $e^{4}He\pi^{0}$. We do not specifically apply energy loss 
and multiple scattering in our fastmc, but we do apply resolution effects based 
on experimental data that include both effects. The plots in figure 
\ref{fig:comp_He} show the comparison between data and simulation in terms of 
theta, $phi$ and momentum of the $^{4}$He DVCS nuclei, that will presented in 
details in the following chapter. The other particles, ($e^{-}$, $p$, 
$\gamma$), are fed to GSIM through the previously mentioned 
simulation-reconstruction chain procedures.

\begin{figure}[tpb]
   \includegraphics[height=5.0cm]{fig_rtpc/updates/He_theta.png}
   \includegraphics[height=5.0cm]{fig_rtpc/updates/He_phi.png}
   \centering
   \includegraphics[height=5.0cm]{fig_rtpc/updates/He_mom.png}
   \caption{Comparison between experimental (blue) and simulated (red) DVCS 
   $^{4}$He nuclei in terms of polar angle, azimuthal angle and momentum.}
   \label{fig:comp_He}
\end{figure}

### 2016-08-23 analysis-note-v2/experimental_setup.tex
more updates to the RTPC and the DVCS checks, and updated the ALU tables after the 4D background subtraction

The IC is constructed from 424 lead-tungstate (PbWO$_{4}$) crystals. Each 
crystal is 16 cm long (corresponding to 17 radiation lengths) with a 
1.33~$\times$~1.33 cm$^2$ front surface and a 1.6~$\times$~1.6 cm$^2$ back 
surface. The energy resolution is around 3$\%$ for photon energies between 2 
GeV and 5 GeV and the angular resolution is between 3 to 5 mrad for the same 
energy range \cite{Hyon-suk}.

>>>>

The IC is constructed from 424 lead-tungstate (PbWO$_{4}$) crystals. Each 
crystal is 16 cm long (corresponding to 17 radiation lengths) with a 
1.33~$\times$~1.33 cm$^2$ front surface and a 1.6~$\times$~1.6 cm$^2$ back 
surface. The energy resolution is around 3 to 4$\%$ for photon energies between 
2 GeV and 5 GeV and the angular resolution is between 3 to 5 mrad for the same 
energy range \cite{Hyon-suk}.
